### 2022-05-22 doc/src/MSLevel.tex
Newly writable bits of sie (or vsie) have unspecified value

>>>>

If a bit of \z{mideleg}/\z{midelegh} is zero and the corresponding bit
in \z{mvien}/\z{mvienh} is changed from zero to one, then the value
of the matching bit in \z{sie}/\z{sieh} becomes {\unspecified}.
Likewise, if a bit of \z{mvien}/\z{mvienh} is one and the corresponding
bit in \z{mideleg}/\z{midelegh} is changed from one to zero, the value
of the matching bit in \z{sie}/\z{sieh} again becomes {\unspecified}.

### 2022-05-22 doc/src/VSLevel.tex
Newly writable bits of sie (or vsie) have unspecified value

>>>>

If a bit of \z{hideleg}/\z{hidelegh} is zero and the corresponding bit 
in \z{hvien}/\z{hvienh} is changed from zero to one, then the value 
of the matching bit in \z{vsie}/\z{vsieh} becomes {\unspecified}.
Likewise, if a bit of \z{hvien}/\z{hvienh} is one and the corresponding 
bit in \z{hideleg}/\z{hidelegh} is changed from one to zero, the value
of the matching bit in \z{vsie}/\z{vsieh} again becomes {\unspecified}.
